Factoring with $n+2$ clean qubits and $n-1$ dirty qubits

### 2017-05-08 paper/doc/paper.tex

See figure \ref{fig:controlled-pivot-flip} for our pivot-flip construction.
For states that are less than the pivot $A$, the comparison against the pivot keeps toggling the ancilla and exactly one of the controlled subtract-and-inverts will fire.
For other states, the ancilla does not change and so the subtract-and-inverse happens either no times or two times (undoing itself) for a net effect of no effect.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-const-pivot-flip.png}
  \caption{\em
    Controlled pivot-flip circuit with a constant pivot.
    Uses $2$ dirty ancilla, $O(c + n)$ gates, and $O(c + n)$ depth where $c$ is the number of controls and $n$ is the register size.
  }
  \label{fig:controlled-pivot-flip}
\end{figure}

@@

Bit permuting operations can usually be emulated by re-labelling qubits, so they are easy to overlook in circuits.
But some of our circuit diagrams have used controlled bit rotations, requiring actual operations, so we provide the constructions for completeness.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-bit-rotate.png}
  \caption{\em
    A controlled bit rotation / bit swap is three controlled bit-reverses.
    Uses no ancilla, $O(n+c)$ gates, and $O(n+c)$ depth.
  }
  \label{fig:dependencies}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-reverse.png}
  \caption{\em
    An inline controlled bit order reversal.
    Each XOR operation is a series of independent CNOTs (note that the inputs have opposite endian-ness to the outputs).
    For reversals on an even number of bits, swap the center two bits beforehand then use one of them as the center workspace bit from this construction.
    Uses no ancilla, $O(c + n)$ gates, and $O(c + n)$ depth.
  }
  \label{fig:dependencies}
\end{figure}

>>>>

See figures \ref{fig:controlled-pivot-flip} and \ref{fig:controlled-const-pivot-flip} for the circuit diagrams.
For states that are less than the pivot $A$, the comparison against the pivot keeps toggling the ancilla and exactly one of the controlled subtract-and-inverts will fire.
For other states, the ancilla does not change and so the subtract-and-inverse happens either no times or two times (undoing itself) for a net effect of no effect.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-const-pivot-flip.png}
  \caption{\em
    Controlled pivot-flip circuit with a constant pivot.
    Uses $2$ dirty ancilla, $O(c + n)$ gates, and $O(c + n)$ depth where $c$ is the number of controls and $n$ is the register size.
  }
  \label{fig:controlled-const-pivot-flip}
\end{figure}

@@

Bit permuting operations can usually be emulated by re-labelling qubits, so they are easy to overlook in circuits.
But some of our circuit diagrams have used controlled bit rotations, requiring actual operations, so we provide the constructions in figures \ref{fig:bit-rotate} and \ref{fig:bit-reverse} for completeness.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-bit-rotate.png}
  \caption{\em
    A controlled bit rotation / bit swap is three controlled bit-reverses.
    Uses no ancilla, $O(n+c)$ gates, and $O(n+c)$ depth.
  }
  \label{fig:bit-rotate}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-reverse.png}
  \caption{\em
    An inline controlled bit order reversal.
    Each XOR operation is a series of independent CNOTs (note that the inputs have opposite endian-ness to the outputs).
    For reversals on an even number of bits, swap the center two bits beforehand then use one of them as the center workspace bit from this construction.
    Uses no ancilla, $O(c + n)$ gates, and $O(c + n)$ depth.
  }
  \label{fig:bit-reverse}
\end{figure}
